Embodied Neuromorphic Benchmarks

### 2015-08-10 paper/paper.tex
typos/formatting

However, \emph{not} using a real physical embodiment for testing is also
problematic.  First and foremost, without an actual real-world task, why
should anyone have any confidence that the performance on the benchmark is
reflective of the actual usefulness of the neuromorphic hardware?  It is
very widely known that \emph{simulations of robots} (or other physical systems) are
often much easier to control and better-behaved than the real thing.  The
field of robotics is filled with algorithms that work well ``in theory,'' but
fail when run on actual hardware.  We do not want a benchmark that falls into
this trap of failing to generalize to real situations.

@@

To address this problem, Nicholas Jacobi proposed the creation of
``minimal'' simulations.  These are simulations where there is variability
\emph{within the simulation itself}.  In other words, we make \emph{poor}
simulations, but ensure that the way in which it is poor is itself
variable.  We then make sure that the controllers work across that whole
range of variability.  ``Instead of trying to eliminate the differences between
simulation and reality, they are acknowledged, and mechanisms are put in place
to prevent evolving controllers from relying on them.'' [ref: jacobi thesis].

@@

It is also worth noting that a minimal simulation \emph{only has to be a
good simulation for successful behaviour}.  That is, ``if we are evolving 
corridor following behaviour, the dynamics of the simulation might
differ wildly from those of reality if the controller hits a wall or
goes round in circles, but this does
not matter, since the controllers we are interested in transferring
across the reality gap will neither
hit walls nor go round in circles.''  If the controller is poor, we do not 
need the simulation to be at all accurate in exactly \emph{how} that poor
behaviour is manifest.  We do not need an exact detailed physics model of
the collision between a robot and a wall, or a detailed model of what happens
to a robot arm when it starts oscillating wildly due to a poor control signal.
All we need is for the simulation to be just good enough to indicate that
things have gone wrong, and thus give a low score to that controller.  This
means that, for example, in a minimal simulation of an eight-legged walking robot,
it is not necessary to have a physics simulation that correctly models what
happens when two legs collide with each other.  Rather, if legs collide
with each other, that is an indication that the walking behaviour is very poor,
so as long as that result is indicated we can greatly simplify the simulation
by not including all the details necessary to deal with these sorts of physical
interactions.

@@

It is important to note that there is actually a theoretical advantage to
using cheap robotics hardware for benchmarking, in addition to the practical
advantages.  In particular, we \emph{don't want benchmarks that rely on
particular high-speed, high-accuracy devices}.  The purpose of the benchmark
is not to indicate how well this neuromorphic hardware works to control this
one particular robot in this task.  Rather, the purpose of a benchmark is to
characterise how well this neuromorphic hardware works on this task 
\emph{in general}.  The variability in the minimal simulation means that it
should be able to function across a wide variety of physical embodiments, and
so if we are to choose one particular physical embodiment to test in the
real world, then we should choose one that is not extremely high-precision.
For this reason, we believe using cheap Lego robot is actually more useful
for benchmarking than an expensive high-precision robot.\footnote{Of course,
for more complex benchmark tasks we may need sensory and motor capabiities
that are beyond that of a simple Lego robot.}

@@

However, if the neuromorphic hardware being benchmarked does not have the
ability to update weights online using a learning rule of this form, then there
are two solutions.  First, the multiplication by $d$ could be done on the
output from the neuromorphic hardware.  There has to be some system to take
the neural output from the hardware and send it to the motor (or the simulation
of the motor).  Instead of outputing the result of $Ad$, the hardware could
output $A$ (the activity of all the neurons), and the interface to the motor
could be responsible for doing the multiplication by $d$ and updating $d$
according to the learning rule.

@@

The result is not meant to be a simulation of a particular physical embodiment.
Rather, the variability in this simulation is meant to be extremely fast
to simulation, and to make it hard to ``cheat''
to control it.  In other words, if a controller manages to be able to control
the various randomly created minimal simulations of embodiment that are
generated with this approach, then we have reason to believe that it will also
be successful at controlling real embodiments.  With this simulation and
modern computers, we can easily simulate in real-time systems with dozens of joints and
highly complex interactions between them, and measure how well an adaptive
controller deals with these situations.

@@

Of course, we need physical confirmation that the minimal simulation defined
in the previous section does a reasonable job.  For this, we define a
particular easy-to-build example of a system that can be usefully controlled
by this adaptive method.  For this, we use the Lego Mindstorms EV3 robot kit.

>>>>

However, \emph{not} using a real physical embodiment for testing is also
problematic.  First and foremost, without an actual real-world task, why
should anyone have any confidence that the performance on the benchmark is
reflective of the actual usefulness of the neuromorphic hardware?  It is
very widely known that simulations of robots (or other physical systems) are
often \emph{much} easier to control and better-behaved than the real thing.  The
field of robotics is filled with algorithms that work well ``in theory,'' but
fail when run on actual hardware.  We do not want a benchmark that falls into
this trap of failing to generalize to real situations.

@@

To address this problem, \cite{Jakobi97evolutionaryrobotics} proposed the creation of
``minimal'' simulations.  These are simulations where there is variability
\emph{within the simulation itself}.  In other words, we make \emph{poor}
simulations, but ensure that the way in which it is poor is itself
variable.  We then make sure that the controllers work across that whole
range of variability.  ``Instead of trying to eliminate the differences between
simulation and reality, they are acknowledged, and mechanisms are put in place
to prevent evolving controllers from relying on them.'' [ref: jacobi thesis].

@@

It is also worth noting that a minimal simulation only has to be a
good simulation \emph{for successful behaviour}.  That is, ``if we are evolving 
corridor following behaviour, the dynamics of the simulation might
differ wildly from those of reality if the controller hits a wall or
goes round in circles, but this does
not matter, since the controllers we are interested in transferring
across the reality gap will neither
hit walls nor go round in circles.''  If the controller is poor, we do not 
need the simulation to be at all accurate in exactly \emph{how} that poor
behaviour is manifest.  We do not need an exact detailed physics model of
the collision between a robot and a wall, or a detailed model of what happens
to a robot arm when it starts oscillating wildly due to a poor control signal.
All we need is for the simulation to be just good enough to indicate that
things have gone wrong, and thus give a low score to that controller.  This
means that, for example, in a minimal simulation of an eight-legged walking robot,
it is not necessary to have a physics simulation that correctly models what
happens when two legs collide with each other.  Rather, if legs collide
with each other, that is an indication that the walking behaviour is very poor,
so as long as that result is indicated we can greatly simplify the simulation
by not including all the details necessary to deal with these sorts of physical
interactions.

@@

It is important to note that there is actually a theoretical advantage to
using cheap robotics hardware for benchmarking, in addition to the practical
advantages.  In particular, we \emph{don't want benchmarks that rely on
high-speed, high-accuracy devices}.  The purpose of the benchmark
is not to indicate how well this neuromorphic hardware works to control this
one particular robot in this task.  Rather, the purpose of a benchmark is to
characterise how well this neuromorphic hardware works on this task 
\emph{in general}.  The variability in the minimal simulation means that it
should be able to function across a wide variety of physical embodiments, and
so if we are to choose one particular physical embodiment to test in the
real world, then we should choose one that is not extremely high-precision.
For this reason, we believe using cheap Lego robot is actually more useful
for benchmarking than an expensive high-precision robot.\footnote{Of course,
for more complex benchmark tasks we may need sensory and motor capabiities
that are beyond that of a simple Lego robot.}

@@

However, if the neuromorphic hardware being benchmarked does not have the
ability to update weights online using a learning rule of this form, then there
are two solutions.  First, the multiplication by $d$ could be done on the
output from the neuromorphic hardware.  There has to be some system to take
the neural output from the hardware and send it to the motor (or to the simulation
of the motor).  Instead of outputing the result of $Ad$, the hardware could
output $A$ (the activity of all the neurons), and the interface to the motor
could be responsible for doing the multiplication by $d$ and updating $d$
according to the learning rule.

@@

The result is not meant to be a simulation of a particular physical embodiment.
Rather, the variability in this simulation is meant to be extremely fast
to simulate, and to make it hard to ``cheat''
to control it.  In other words, if a controller manages to be able to control
the various randomly created minimal simulations of embodiment that are
generated with this approach, then we have reason to believe that it will also
be successful at controlling real embodiments.  With this simulation and
modern computers, we can easily simulate in real-time systems with dozens of joints and
highly complex interactions between them, and measure how well an adaptive
controller deals with these situations.

@@

Of course, we need physical confirmation that the minimal simulation defined
in the previous section does a reasonable job.  For this, we define a
particular easy-to-build example of a system that can be usefully controlled
by this adaptive method.  In particular, we use the Lego Mindstorms EV3 robot kit.
